Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-09-05 main_theorem.tex
Finished writting up lem:Lan_preserve_colim and prepared main_theorem.tex that encapsulates the main definitions and results.

\documentclass[../text.tex]{subfiles}

@@

@@

\subsection{Definition of Factorization Algebras}

Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones. The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs. These were geometric in nature. The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics. Here we will present these ideas following \cite{cg2016} and also \cite{af_primer}. A similar exposition can be found in \cite{ginot2015}.

\begin{remark}
    We note that we have fixed a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the $\infty$-category that our algebras will be valued in.
\end{remark}

@@

\begin{remark}
    It is obvious that in the case of (stratified) manifolds we have already seen alternative notation for the $\infty$-operad $\opens(X)$ before, namely $\mfld[r]_{/M}$. This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
\end{remark}

@@

    We also get out that an algebra morphism $\phi: F \rightarrow G$ is simply a family of maps $\phi(U): F(U) \rightarrow G(U)$ for each open set $U$, such that it respects the operations of the algebra. Namely, for each multi-morphism $\{ U_i \}_{i \in I} \rightarrow U$ there is a commuting square
    %
    \begin{equation}\label{cd:fa_morphisms}
        \begin{tikzcd}[row sep=large, column sep = large]
            \bigotimes\limits_{i \in I} F(U_i) \arrow[r, "F(\{ U_i\} {,} U)"] \arrow[d, "\bigotimes\limits_{i \in I} \phi(U_i)"'] & F(U) \arrow[d, "\phi(U)"] \\
            \bigotimes\limits_{i \in I} G(U_i) \arrow[r, "G(\{ U_i\} {,} U)"'] & G(U).
        \end{tikzcd}
    \end{equation}

\end{remark}

\begin{remark}\label{rem:op_to_op}
    There is an obvious inclusion functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
\end{remark}

A factorization algebra will be a prefactorization algebra that further satisfies a certain gluing condition that lets us construct its value on `larger' sets if we know it on `smaller' sets. More formally, this will be a kind of cosheaf condition, that we describe now, following \cite{weiss1999,af_primer}.

@@

\begin{remark}
    In other words, $F$ is a Weiss cosheaf if it is a functor that sends colimits (which, in this case, are unions) of Weiss covers $\{ U_i \xhookrightarrow{} U \}_{i \in I}$ to colimits in $\catC$
    %
    \begin{equation}
        F(U) \simeq F \bigg( \bigcup_{i \in I} U_i \bigg) \simeq \mathrm{colim}_{i \in I} F(U_i).
    \end{equation}
\end{remark}

@@

\begin{definition}
    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$}\footnote{These are called homotopy factorization algebras in \cite{cg2016}, however we do not consider the lax version of factorization algebras that they also present.} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \falg_X (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\opens[s](X)}(\catC) \arrow[d] \\
            \csheaves[W]_X(\catC) \arrow[r] & \mathsf{Fun}(\opens[r](X), \catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

@@

\begin{remark}\label{rem:check_nerve}
    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf. This means that the definition can be rewritten in an equivalent way as with all cosheaves. Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve. Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
    %
    \begin{equation}
        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
    \end{equation}
    %
    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
    %
    \begin{equation}
        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
    \end{equation}
    %
    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
    %
    \begin{equation}
        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
    \end{equation}
    %
    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
\end{remark}

@@

There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here. In our case one can also take a perspective more akin to \cite[def.A.1.12]{lurie_ha} by defining locally constant cosheaves and then pulling back this property to factorization algebras. This is what we will do, along with focusing our attention to stratified (and therefore also to smooth) manifolds. The definitions we will make can in a lot of cases also be expanded for any $C^0$ stratified space or topological manifold.

@@

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for (locally constant) factorization algebras. We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not. We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case. To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps. First we have the following results:
%
\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
\end{proposition}
%
\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
%
\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
\end{theorem}
%
\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}
%
The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying $\infty$-operads. However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition. The theorems that we present in this section are immensely helpful in relating factorization algebras to results in the area of disk algebras, which will be obvious throughout the rest of this work. One important example that we will see is in \Cref{ch:gluing_disk_alg}.

In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits.

@@

%To show the equivalence, we follow a related strategy to the one laid out in part 2 of the proof of \cite[Prop.2.22]{af_primer}.

@@

The following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
%
\begin{lemma}\label{lem:Lan_preserve_colim}
    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of (locally small) $\infty$-categories, where $\mathscr{M}$ and $\catC$ are cocomplete. Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$. $L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
    %
    \begin{align}
        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
    \end{align}
    %
    does so.
\end{lemma}

\begin{proof}
    We use the standard notation $y_{\mscr{X}}=h_\bullet\colon\mscr{X}\to\msf{PShv}(\mscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mscr{X}$ [see Kerodon Definition II.8.3.3.9/03NF; Proposition II.8.3.3.2/03N2]. First, note that a left Kan extension of type
    \[
        L_{y_{\mscr{D}}}F\colon\msf{PShv}(\mscr{D})\to\mscr{C}
    \]
    preserves colimits as a consequence of [Kerodon Theorem II.8.4.3.6/03WH]. 
    Next, we claim that there is an equivalence of functors
    \begin{equation}\label{WZUZC5F}
        L_{\iota}(F)\simeq L_{y_{\mscr{D}}}(F)\circ L_{\iota}(y_{\mscr{D}}).
    \end{equation}
    as functors $\mscr{M}\to\mscr{C}$. Indeed, consider the diagram 
    \[
        \begin{tikzcd}[sep=large]
             & \mscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mscr{D}}}"]\\
            \mscr{M}\ar[rr,bend right=40,"{L_{\iota}(F)}"']\ar[r,"{L_{\iota}(y_{\mscr{D}})}"'] &[4em] \msf{PShv}(\mscr{D})\ar[r,"{L_{y_{\mscr{D}}}(F)}"'] & \mscr{C}
        \end{tikzcd}
    \]
    and note that by [Kerodon Theorem II.8.4.0.3/03W9 and Theorem II.8.4.3.6/03WH] there is an isomorphism $L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}}\cong F$ which commutes the right triangle. Consequently, using [Kerodon Remark 7.3.1.10/02YH], we have $L_{\iota}(F)\simeq L_{\iota}(L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}})$. Since $L_{y_{\mscr{D}}}(F)$ preserves colimits, we have $L_{\iota}(L_{y_{\mscr{D}}}(F)\circ y_{\mscr{D}})\simeq L_{y_{\mscr{D}}}(F)\circ L_{\iota}(y_{\mscr{D}})$, obtaining \eqref{WZUZC5F}.

    Finally, we claim
    \begin{equation}\label{D9NQYMT}
        L_{\iota}(y_{\mscr{D}})\simeq T_{\iota}=\iota^*\circ y_{\mscr{M}}
    \end{equation}
    as functors $\mscr{M}\to\msf{PShv}(\mscr{D})$, which will imply the Lemma by \eqref{WZUZC5F}. To prove \eqref{D9NQYMT}, let us observe that $L_{\iota}(y_{\mscr{D}})\simeq L_{y_{\mscr{M}}}(L_{\iota}(y_{\mscr{D}}))\circ y_{\mscr{M}}$ similarly to the above, and that $L_{y_{\mscr{M}}}(L_{\iota}(y_{\mscr{D}}))\simeq L_{y_{\mscr{M}}\circ\iota}(y_{\mscr{D}})$ by [Kerodon Proposition II.7.3.8.18/031M]. Thus, it suffices to show that $\iota^*\simeq L_{y_{\mscr{M}}\circ\iota}(y_{\mscr{D}})$. 
\end{proof}

@@

    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}. Thus, we only need to show that the functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$ preserves Weiss colimits. Namely, we need to show that there is an equivalence
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv} (\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e),
    \end{equation}
    %
    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can equivalently be written as
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
    \end{equation}}
    %
    But this is exactly the result of \Cref{lem:gluing_disk/M/e}.
\end{proof}

@@

\begin{remark}
    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
\end{remark}

\begin{remark}
    A version of \Cref{thm:disk_alg=lcfa} was proven as \cite[thm.6]{gtz2014} in the case of smooth manifolds. The proof there, however, made crucial use of choosing a Riemannian metric on the manifold and constructing geodesically convex neighborhoods. This technique is, at least presently, not extendable to the stratified case, but our proof above subverts the need for it. 
\end{remark}

\begin{remark}
    As noted at the beginning of \S2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, though typically not all, of the global observables. The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theories. 
\end{remark}

>>>>

% Run only with XeLaTeX!
%---------------------------------------------------------------------
%	FORMATING AND TYPESETTING
%---------------------------------------------------------------------

% Set document class
\documentclass[12pt,a4paper]{article}

% Option to change margin size
\usepackage[margin=2cm]{geometry}

% Font and encoding settings
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc} not necessary with xelatex?
\usepackage{yfonts} % germanic fonts (fraktur...)
%\defaultfontfeatures{Ligatures=TeX} %??

% Footnotes
\usepackage[stable]{footmisc}

% Indentation and spacing
\usepackage{indentfirst} % indentation
\usepackage{enumitem}[leftmargin=0pt] % spacing
\setlist{nosep}

% Multi column environment
\usepackage{multicol}

% Formating of titles
\usepackage{titlesec}
\titleformat{\section}
{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
{\normalfont\small\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]
{\normalfont\small\bfseries}{\theparagraph}{1em}{}
\titleformat{\subparagraph}[runin]
{\normalfont\small\bfseries}{\thesubparagraph}{1em}{}
\usepackage[titletoc]{appendix}

% Math typesetting packages
\usepackage{amsmath, amssymb, amsthm, mathtools, commath}
\usepackage[warnings-off={mathtools-colon,mathtools-overbracket}]{unicode-math} % makes \mathbb{1} work and changes font of mathbb
\usepackage[mathscr]{euscript} % euler script font
\usepackage{tikz-cd} % tikz commutative diagrams
\usepackage{thmtools, thm-restate} % theorem tools, especially restatable

\AtBeginDocument{\renewcommand\setminus{\smallsetminus}} % \setminus doesn't work in unicode-math

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	GRAPHICS
%---------------------------------------------------------------------

\usepackage{float}
\usepackage{caption}
\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{pdfpages} % for inserting pdf pages

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	BIBLIOGRAPHY
%---------------------------------------------------------------------

\usepackage[backend=biber,style=alphabetic]{biblatex}
\renewcommand*{\bibfont}{\small}
\addbibresource{text.bib}

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	HYPERLINKS
%---------------------------------------------------------------------

% Define the colors
\usepackage{xcolor}
\definecolor{brown}{HTML}{CD853F}
\definecolor{blue}{HTML}{4169E1}
\definecolor{green}{HTML}{2E8B57}

% Setup options for hyperlinks
\usepackage{hyperref}
\hypersetup{
colorlinks=true, linkcolor=black, breaklinks=true,
linktoc=all, bookmarksnumbered=true,
urlcolor=brown, linkcolor=blue, citecolor=green, % Link colors
}

% Referencing package
\usepackage{cleveref}
\crefname{section}{\S\!}{\S\S\!}
\Crefname{section}{\S\!}{\S\S\!}

%---------------------------------------------------------------------
%	THEOREM STYLES
%---------------------------------------------------------------------

% Define a dummy counter to keep count for all sub-environments
\newcounter{counter} \numberwithin{counter}{section}

% Define theorem styles here based on the definition style
\theoremstyle{definition}
\newtheorem{definition}[counter]{Definition}
\newtheorem{construction}[counter]{Construction}
\newtheorem{observation}[counter]{Observation}

% Define theorem styles here based on the plain style
\theoremstyle{plain} 
\newtheorem{theorem}[counter]{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[counter]{Corollary}
\newtheorem{lemma}[counter]{Lemma}
\newtheorem{proposition}[counter]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{conjecture}[counter]{Conjecture}

% Define theorem styles here based on the remark style
\theoremstyle{remark}
\newtheorem{example}[counter]{Example}
\newtheorem{remark}[counter]{Remark}

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	NEW COMMANDS
%---------------------------------------------------------------------

% general target category
\newcommand{\catC}{\mathscr{C}}

% categories of factorization algebras
\newcommand{\falg}{\mathscr{F} \mathsf{Alg}}
\newcommand{\lcfa}{\mathscr{F} \mathsf{Alg}^{\mathsf{lc}}}

% category of manifolds
\newcommand{\mfld}[1][s]{%
    \ifx r#1\mathsf{Mfld}\else
    \ifx s#1\mathscr{M} \mathsf{fld}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of disks
\newcommand{\disk}[1][s]{%
    \ifx r#1\mathsf{Disk}\else
    \ifx s#1\mathscr{D} \mathsf{isk}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of opens
\newcommand{\opens}[1][s]{%
    \ifx r#1\mathsf{Opns}\else
    \ifx s#1\mathscr{O} \mathsf{pns}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of cosheaves
\newcommand{\csheaves}[1][n]{%
    \ifx n#1 \mathsf{c} \mathscr{S} \mathsf{hv}\else
    \mathsf{c} \mathscr{S} \mathsf{hv}^{\mathsf{#1}}
    \fi
}

% category of infinity categories
\newcommand{\cat}{\mathscr{C} \mathsf{at}_{\infty}}

% template for category of algebras
\newcommand{\alg}[1]{\mathscr{A} \mathsf{lg}_{#1}}

% template for category of locally constant algebras
\newcommand{\lcalg}[1]{\mathscr{A} \mathsf{lg}^{\mathsf{lc}}_{#1}}

% half-open interval
\newcommand{\hoint}{\mathbb{R}_{\geq 0}}

% Cech complex
\newcommand{\cech}{\check{\mathsf{C}}}

% Category of basics
\newcommand{\bsc}{\mathscr{B} \mathsf{sc}}
\newcommand{\bstr}{\mathscr{B}}

% Open cone
\newcommand{\cone}[1][n]{%
    \ifx b#1\overline{\mathsf{C}}\else
    \ifx n#1\mathsf{C}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

\newcommand{\lrangle}[1]{\langle #1 \rangle}

%---------------------------------------------------------------------

\usepackage{subfiles}

%\setcounter{section}{-1}

@@

% Set title, author and date
\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
\author{Aleksandar Ivanov, Ödül Tetik}
\date{}
\maketitle

@@

\subsection{Definition of Factorization Algebras}
    We fix a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the target $\infty$-category.

@@

@@

    We also get out that an algebra morphism $\phi: F \rightarrow G$ is simply a family of maps $\phi(U): F(U) \rightarrow G(U)$ for each open set $U$, such that it respects the operations of the algebra. Namely, for each multi-morphism $\{ U_i \}_{i \in I} \rightarrow U$ there is a commuting square
    %
    \begin{equation}\label{cd:fa_morphisms}
        \begin{tikzcd}[row sep=large, column sep = large]
            \bigotimes\limits_{i \in I} F(U_i) \arrow[r, "F(\{ U_i\} {,} U)"] \arrow[d, "\bigotimes\limits_{i \in I} \phi(U_i)"'] & F(U) \arrow[d, "\phi(U)"] \\
            \bigotimes\limits_{i \in I} G(U_i) \arrow[r, "G(\{ U_i\} {,} U)"'] & G(U).
        \end{tikzcd}
    \end{equation}
\end{remark}

@@

@@

\begin{definition}
    The $\infty$-category of \emph{($\catC$-valued) factorization algebras on $X$} is the full $\infty$-subcategory of $\alg{\opens[s](X)}$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \falg_X (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \alg{\opens[s](X)}(\catC) \arrow[d] \\
            \csheaves[W]_X(\catC) \arrow[r] & \mathsf{Fun}(\opens[r](X), \catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

@@

@@

@@

Now that we have introduced all the varieties of factorization algebras, it's a natural and useful question to ask what the $\infty$-operad governing them is. For prefactorization algebras, the answer comes by definition, but this is not the case for factorization algebras, locally constant or not. We will be working in the generality of stratified manifolds, and all our results in this section will come in pairs, one for the locally constant case and one not. We call the results in the not-necessarily-locally-constant case corollaries since their proofs will be obvious from the proofs of the statements in the locally constant case. To connect factorization algebras to the theory of algebras over an $\infty$-operad we will work in two steps. First we have the following results:
%
\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$.
\end{proposition}
%
\begin{corollary}\label{cor:fh_disk_to_falg}
    Given a stratified manifold $M$ factorization homology provides a functor
    %
    \begin{equation}
        \int: \alg{\disk[r]_{/M}} (\catC) \xrightarrow{\ \ \ \ } \falg_{M} (\catC).
    \end{equation}
\end{corollary}

The second step is then showing that the functors constructed above are equivalences, which we summarize in the following results:
%
\begin{theorem}\label{thm:disk_alg=lcfa}
    For each stratified manifold $M$, the previously constructed factorization homology functor provides an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \lcfa_M (\catC)
    \end{equation}
    %
    between $\disk_{/M}$-algebras and locally constant factorization algebras on $M$. Equivalently, the $\infty$-operad governing locally constant factorization algebras can be taken to be $\disk_{/M}$.
\end{theorem}
%
\begin{corollary}\label{cor:disk_alg=falg}
    The $\infty$-operad governing factorization algebras on a stratified manifold $M$ can be taken to be $\disk[r]_{/M}$,
    %
    \begin{equation}
        \alg{\disk[r]_{/M}} (\catC) \xrightarrow[\int]{\ \ \simeq \ \ } \falg_M (\catC).
    \end{equation}
\end{corollary}
%
The reason for the phrasing in these results is that, technically speaking, equivalence of the $\infty$-categories of algebras does not imply equivalence of the underlying $\infty$-operads. However since we only defined (locally constant) factorization algebras at the level of algebras and not at the level of $\infty$-operads, we can take the operadic definition as the basic one, and interpret the results as connecting this to the classical definition.

In the service of working towards proofs of all of these results we first have to pause and develop some necessary technically results regarding Weiss covers and preservation of colimits, as well as record a known fact about the relative versions of the $\infty$-operads in play. We start with this fact first.

\begin{lemma}\label{lem:double_slice}
    Every open embedding $e: N \xhookrightarrow{} M$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        (\mfld_{/M})_{/e} \simeq \mfld_{/N}.
    \end{equation}
    %
    The same holds for $\mfld[r]$, as well as, $\disk$ and $\disk[r]$.
\end{lemma}

@@

@@

A suggestion regarding the following lemma about preservation of colimits is sketched out in \cite{rezk2023lan}.
%
\begin{lemma}\label{lem:Lan_preserve_colim}
    Let $F: \mathscr{D} \xrightarrow{} \catC$ and $\iota: \mathscr{D} \xrightarrow{} \mathscr{M}$ be functors of $\infty$-categories, where $\mathscr{D}$ is essentially small, while $\mathscr{M}$ and $\catC$ are locally small and cocomplete. Let $L_{\iota} F: \mathscr{M} \xrightarrow{} \catC$ be the left Kan extension of $F$ along $\iota$. $L_{\iota} F$ preserves a given colimit if, and only if, the restricted Yoneda embedding
    %
    \begin{align}
        T_{\iota}: \mathscr{M} \xrightarrow{\ y_{\mathscr{M}} \ } \mathsf{PShv}(\mathscr{M}) \xrightarrow{\ \iota^* \ } \mathsf{PShv}(\mathscr{D}) 
    \end{align}
    %
    does so.
\end{lemma}

\begin{proof}
    We use the standard notation $y_{\mathscr{X}}=h_\bullet\colon\mathscr{X}\to\mathsf{PShv}(\mathscr{X})$ for `the' covariant Yoneda embedding of a locally small $\infty$-category $\mathscr{X}$ (see \cite[\href{https://kerodon.net/tag/03NF}{03NF},\href{https://kerodon.net/tag/03N2}{03N2}]{lurie_kerodon}). First, note that a left Kan extension of type
    %
    \begin{equation}
        L_{y_{\mathscr{D}}}F \colon \mathsf{PShv}(\mathscr{D}) \xrightarrow{\ \ \ \ } \mathscr{C}
    \end{equation}
    %
    preserves colimits as a consequence of \cite[\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon}. Next, we claim that there is an equivalence
    %
    \begin{equation}\label{WZUZC5F}
        L_{\iota}F \simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}
    \end{equation}
    %
    as functors $\mathscr{M} \to \mathscr{C}$. Indeed, consider the diagram
    % 
    \begin{equation}
        \begin{tikzcd}[sep = large]
            & \mathscr{D}\ar[dl,"{\iota}"']\ar[dr,"{F}"]\ar[d,"{y_{\mathscr{D}}}"]\\
            \mathscr{M}\ar[rr,bend right=40,"{L_{\iota}F}"']\ar[r,"{L_{\iota}y_{\mathscr{D}}}"'] &[4em] \mathsf{PShv}(\mathscr{D})\ar[r,"{L_{y_{\mathscr{D}}}F}"'] & \mathscr{C},
        \end{tikzcd}
    \end{equation}
    %
    and note that by \cite[\href{https://kerodon.net/tag/03W9}{03W9},\href{https://kerodon.net/tag/03WH}{03WH}]{lurie_kerodon} there is an equivalence (actually even an isomorphism) $L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}} \simeq F$ which commutes the right triangle. Consequently, using \cite[\href{https://kerodon.net/tag/02YH}{02YH}]{lurie_kerodon}, we have $L_{\iota}F \simeq L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})$. Since $L_{y_{\mathscr{D}}}F$ preserves colimits, we have $L_{\iota}(L_{y_{\mathscr{D}}}F \circ y_{\mathscr{D}})\simeq L_{y_{\mathscr{D}}}F \circ L_{\iota}y_{\mathscr{D}}$, obtaining \Cref{WZUZC5F}.

    Finally, we claim
    %
    \begin{equation}\label{D9NQYMT}
        L_{\iota}y_{\mathscr{D}} \simeq T_{\iota} := \iota^* \circ y_{\mathscr{M}}
    \end{equation}
    %
    as functors $\mathscr{M} \to \mathsf{PShv}(\mathscr{D})$, which will imply the Lemma by \Cref{WZUZC5F}. By \cite[\href{https://kerodon.net/tag/03WN}{03WN}]{lurie_kerodon} we have the following diagram in which the triangle commutes
    %
    \begin{equation}
        \begin{tikzcd}
            \mathscr{M} \arrow[r, "y_{\mathscr{M}}"] & \mathsf{PShv}(\mathscr{M}) \arrow[r, "\iota^*"] \arrow[d, "\top", phantom, very near start] & \mathsf{PShv}(\mathscr{D}) \arrow[ll, "H", bend left] \\
            & {} & \mathscr{D} \arrow[u, "y_{\mathscr{D}}"'] \arrow[llu, "\iota", bend left]
            \end{tikzcd},
    \end{equation}
    %
    so that $H$ is a left adjoint to $\iota^* \circ y_{\mathscr{M}}$. Being a right adjoint, we can write $\iota^* \circ y_{\mathscr{M}}$ as a left Kan extension, which allows for the following calculation
    %
    \begin{equation}
        \iota^* \circ y_{\mathscr{M}} \simeq L_{H}\mathrm{id}_{\mathsf{PShv}(\mathscr{D})} \simeq L_{H}(L_{y_{\mathscr{D}}} y_{\mathscr{D}}) \simeq L_{H \circ y_{\mathscr{D}}}(\mathscr{D}) \simeq L_{\iota}(y_\mathscr{D}),
    \end{equation}
    %
    where for the second equivalence we used the fact that $y_{\mathscr{D}}$ is a dense functor \cite[\href{https://kerodon.net/tag/03W2}{03W2}]{lurie_kerodon} (using the definition of dense functor as in \cite[\href{https://kerodon.net/tag/03VP}{03VP}]{lurie_kerodon}) and in the third equivalence we used \cite[\href{https://kerodon.net/tag/031M}{031M}]{lurie_kerodon}.
\end{proof}

@@

    With the Weiss cosheaf property being a statement about preserving colimits, and with $\int F$ being a left Kan extension we are exactly in the situation of \Cref{lem:Lan_preserve_colim}. Thus, we only need to show that the functor $T: \mfld_{/M} \xrightarrow{} \mathsf{PShv} (\disk_{/M})$ preserves Weiss colimits. Namely, we need to show that there is an equivalence
    %
    \begin{equation}
        \mathsf{colim} \big( \mathscr{U} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{\mathsf{Hom}_{\mfld_{/M}}(\cdot, -)} \mathsf{PShv} (\disk_{/M}) \big) \xrightarrow{\ \ \simeq \ \ } \mathsf{Hom}_{\mfld_{/M}}(\cdot, e),
    \end{equation}
    %
    where on the right-hand side we've used the fact that $\mathscr{U}$ is, in particular, a covering sieve.\footnote{If we also append the straightening--unstraightening construction to $T$, the desired equivalence can be thought of as an equivalence
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld_{/M} \xrightarrow{ (\disk_{/M})_{/-}} \mathsf{RFib}_{\disk_{/M}}) \simeq (\disk_{/M})_{/e}.
    \end{equation}}
    %
    But this is exactly the result of \Cref{lem:gluing_disk/M/e}.
\end{proof}

@@

% Generate bibliography
\newpage
\printbibliography
